State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-15 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to results in prep for meeting with VK

The sensor were model such that they were spaced in a regular square grid where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
% \begin{figure}
% 	\centering
% 		\includegraphics[scale=1]{file.eps}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
% \end{figure}

>>>>

The sensors were modelled such that they were spaced in a regular square grid, where the number of sensors was 100, sensor width $\sigma^2_m$ was 1.44 which equals $2$~mm full width at half maximum, with spacing $\Delta_y$ equal to $2.22$~mm. This arrangement modelled the recording as having some cross talk, which is typical from neurophysiological recordings. Note, sensor design to guarantee representation of the field can be achieved using the frequency analysis from section~\ref{} given access to the true field. \omg{From frequency analysis the separation is $2.77$, with $\rho = 2$ (note same as basis function).}
% \begin{figure}
% 	\centering
% 		\includegraphics[scale=1]{file.eps}
% 	\caption{Example of experimental design and model output. \textbf{A}. Example of the neural field with sensors. The centres of the sensors are shown by crossed and the sensor widths ($1/2$ height of Gaussian) are shown by the circles. \textbf{B} Example of data generated by the model through the observations. \textbf{C}. Power spectral density of the data generated by an observation showing the typical $1/f$ characteristic of iEEG.}
% 	\label{fig:ExampleFieldAndSensorsDataAndPSD}
% \end{figure}
